# The VERIS Community Database
Information sharing is a complex and challenging undertaking. If done correctly, everyone involved benefits from the collective intelligence. If done poorly, it may mislead participants or create a learning opportunity for our adversaries. The Verizon RISK Team supports and participates in a variety of information sharing initiatives and research efforts. We continue to drive the publication of the Verizon Data Breach Investigations Report (DBIR) annually, where we have an unprecedented number of new data-sharing partners, and we are committed to keeping the report publicly available and free to download. We regularly receive inquiries about our dataset, and our ability to share further, but we are limited in what data we can share in raw format due to agreements with our partners and customers.

## The Problem
While there are a handful of efforts to capture security incidents that are publicly disclosed, there is no unrestricted, comprehensive raw dataset available for download on security incidents that is sufficiently rich to support both community research and corporate decision-making. There are organizations that collect—and in some form—disseminate aggregated collections, but they are either not in a format that lends itself to ease of data manipulation and transformation required for research, or the underlying data are not freely and publicly available for use. This gap has long hampered researchers who are studying the problems surrounding security incidents, as well as the risk managers who are starved for reliable data upon which to base their risk calculations.

# Getting Involved
If you want to get involved in this project, we have directions in the wiki for this repo.  If you are new to GitHub, it is the book icon to the right of this page section.

```{r echo=F}
library(verisr)
library(ggplot2)
vcdb <- json2veris("data/json/validated/")


library(verisr)
data('industry2', package='verisr')
vcdb.dir <- "data/json/validated/"
# may optionally load a custom json schema file.
if (interactive()) { # show progress bar if the session is interactive
  vcdb <- json2veris(vcdb.dir, schema="../VCDB/vcdb-merged.json", progressbar=TRUE)
} else {
  vcdb <- json2veris(vcdb.dir, schema="../VCDB/vcdb-merged.json")  
}

library(verisr)
data('industry2', package='verisr')
data_dirs <- c("../VCDB/data/json", "private_data")
veris <- json2veris(data_dirs, schema="path/to/schema.json")



```

# VCDB Statistics

```{r "yearly", echo=F, warning=F, fig.height=4, fig.width=10}

library(ggplot2)
years <- getenum(vcdb, "timeline.incident.year")
yr <- as.numeric(as.character(years$enum))
years <- years[order(yr), ]
years$enum <- factor(years$enum, years$enum, ordered=T)
gg <- ggplot(years, aes(x=enum, y=x, label=x))
gg <- gg + geom_bar(stat="identity", fill="steelblue")
gg <- gg + geom_text(size=3, vjust=-0.4)
gg <- gg + xlab("Year") + ggtitle("Incidents per year")
gg <- gg + scale_y_continuous(expand=c(0,0), limit=c(0, max(years$x*1.05)))
gg <- gg + theme(panel.grid = element_blank(),
                 panel.background = element_blank(),
                 axis.text.y = element_blank(),
                 axis.title.y = element_blank(),
                 legend.position = "none",
                 axis.ticks = element_blank())
print(gg)
```

```{r}

actors <- getenum(vcdb, "actor")
 # actors in a dataframe

actors <- getenum(vcdb, "actor", add.n=TRUE, add.freq=TRUE)
print(actors)

```
data aggregated on a VERIS enumeration. In this case the variety of external actor.
```{r}
ext.variety <- getenumCI(vcdb, "actor.external.variety")
print(ext.variety)
```

```{r}
gg <- ggplot(ext.variety, aes(x=enum, y=x))
gg <- gg + geom_bar(stat="identity", fill="steelblue")
gg <- gg + coord_flip() + theme_bw()
print(gg)

print(simplebar(ext.variety, "Variety of Hacking Actions"))
```

```{r}
# see the docs on data.table for getting columns like this
ddfilter <- vcdb[["attribute.confidentiality.data_disclosure.Yes"]]
webfilter <- vcdb[["action.hacking.vector.Web application"]]
# now we can combine with | or & ("or" and "and" respectively)
# to filter incidents with confirmed data loss and web vector:
ddweb <- ddfilter & webfilter
cat("Confirmed data loss events:", sum(ddfilter), "\n")
cat("Hacking vector of web apps:", sum(webfilter), "\n")
cat("Both data loss and web app:", sum(ddweb), "\n")

```

```{r}

a2 <- getenumCI(vcdb, c("action", "asset.variety", na.rm=TRUE)) # `na.rm=TRUE` means "remove cases where the enumeration isn't applicable from the sample size"
head(a2)

```



```{r}
library(ggplot2)
# take in the vcdb object and the field to plot
verisplot <- function(vcdb, field) {
  # get the data.frame for the field with frequency
  localdf <- getenum(vcdb, field, add.freq=T)
  # now let's take first 5 fields in the data frame.
  localdf <- localdf[c(1:5), ]
  # add a label to the data.frame
  localdf$lab <- paste(round(localdf$freq*100, 0), "%", sep="")
  # now we can create a ggplot2 instance
  gg <- ggplot(localdf, aes(x=enum, y=freq, label=lab))
  gg <- gg + geom_bar(stat="identity", fill="steelblue")
  # add in text, adjusted to the end of the bar
  gg <- gg + geom_text(hjust=-0.1, size=3)
  # flip the axes and add in a title
  gg <- gg + coord_flip() + ggtitle(field)
  # remove axes labels and add bw theme
  gg <- gg + xlab("") + ylab("") + theme_bw()
  # fix the y scale to remove padding and fit our label (add 7%) 
  gg <- gg + scale_y_continuous(expand=c(0,0), 
                                limits=c(0, max(localdf$freq)*1.1))
  # make it slightly prettier than the default
  gg <- gg + theme(panel.grid.major = element_blank(),
                   panel.border = element_blank(),
                   axis.text.x = element_blank(),
                   axis.ticks = element_blank())
}

# try the following (code not in book)
print(verisplot(vcdb, "action"))
print(verisplot(vcdb, "actor.external.variety"))
print(verisplot(vcdb, "action.physical.variety"))
print(verisplot(vcdb, "action.hacking.vector"))
print(verisplot(vcdb, "attribute.confidentiality.data.variety"))
print(verisplot(vcdb, "asset.variety"))
```

```{r}
library(dplyr)
action <- vcdb %>% getenum('action.malware.variety')
action$action <- "Malware"
tmp <- vcdb %>% getenum('action.hacking.variety')
tmp$action <- "Hacking"
action <- bind_rows(action, tmp)
tmp <- vcdb %>% getenum('action.social.variety')
tmp$action <- "Social"
action <- bind_rows(action, tmp)
tmp <- vcdb %>% getenum('action.physical.variety')
tmp$action <- "Physical"
action <- bind_rows(action, tmp)
tmp <- vcdb %>% getenum('action.misuse.variety')
tmp$action <- "Misuse"
action <- bind_rows(action, tmp)
tmp <- vcdb %>% getenum('action.error.variety')
tmp$action <- "Error"
action <- bind_rows(action, tmp)
tmp <- vcdb %>% getenum('action.environmental.variety')
tmp$action <- "Environmental"
action <- bind_rows(action, tmp)
action <- action %>% arrange(desc(x)) %>% select(-freq, -n)
action$n <- dim(vcdb)[1]
action$freq <- round(100 * action$x/action$n, 2)
action[1:20,]
```


```{r}
library(ggplot2)
# get a data.frame comparing the actions to the assets
# this will add zero's in missing squares and include a frequency
a2 <- getenum(vcdb, enum="action", 
              primary="actor.variety",
              add.freq=T)
# trim unknown asset and environment action for space
a2 <- a2[which(a2$enum!="environmental" & a2$primary!="Unknown"), ]
# so we should create a "slim" version without zeros to color it
slim.a2 <- a2[which(a2$x!=0), ]
# could sort these by converting to factors (we did in Fig 7-6)

# now make a nice plot  
gg <- ggplot(a2, aes(x=enum, 
                     y=primary,
                     fill=freq))
gg <- gg + geom_tile(fill="white", color="gray80")
gg <- gg + geom_tile(data=slim.a2, color="gray80")
gg <- gg + scale_fill_gradient(low = "#F0F6FF", 
                               high = "#4682B4", guide=F)
gg <- gg + xlab("") + ylab("") + theme_bw()
gg <- gg + scale_x_discrete(expand=c(0,0))
gg <- gg + scale_y_discrete(expand=c(0,0))
gg <- gg + theme(axis.ticks = element_blank())
# and view it
print(gg)

```


```{r  "a2grid", echo=FALSE, fig.height=6, fig.width=7}
action.asset <- getenumby(vcdb, enum="asset.assets", primary="action")
assetmap <- c("Server", "Network", "User Dev", "Media", 
              "Person", "Kiosk/Term", "Unknown")
action.asset$enum <- factor(action.asset$enum, 
                            levels=rev(assetmap), ordered=T)
action.asset$primary <- factor(action.asset$primary,
                               levels=c("malware", "hacking", "social", 
                                        "misuse", "physical", "error",
                                        "environmental",  "unknown"),
                               ordered=T)
slim.aa <- action.asset[which(action.asset$x>0), ]
gg <- ggplot(action.asset, aes(x = primary, y = enum, fill = x, label = x))
gg <- gg + geom_tile(fill="white", color="gray80")
gg <- gg + geom_tile(data=slim.aa, color="gray80") + geom_text(data=slim.aa)
gg <- gg + scale_fill_gradient(low = "#D8EEFE", high = "#4682B4")
gg <- gg + scale_x_discrete(expand=c(0,0)) + scale_y_discrete(expand=c(0,0))
gg <- gg + ylab("") + xlab("")
gg <- gg + ggtitle("A2 Grid: Assets and Actions")
gg <- gg + theme_bw()
gg <- gg + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=0.5),
                 axis.text = element_text(size=14),
                 axis.ticks = element_blank(),
                 legend.position = "none",
                 plot.background = element_blank(),
                 panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.border = element_rect(colour = "gray30"),
                 panel.background = element_blank())
print(gg)
```

```{r echo=F}
csv.out <- veris2csv(vcdb)
write.csv(csv.out, "data/csv/vcdb.csv", row.names=F)
```

